Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-12 prob.tex
prob.tex \section{Proofs} update a little bit...
prob.tex \section{Proofs} Update the definitions...

\begin{definition}\cite{Hatcher2001}~The unit sphere in $\mathbb{R}^{d}$
is denoted by $S^{d-1}$.\qed\end{definition}

\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ is
called an \emph{approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
if 
\[
W_{l}\le\sideset{_{\mathbb{R}}}{_{i=0}^{d-1}}\sum f\left(\ket{\psi_{i}}\right)\le W_{r}
\]
 for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
of $\mathbb{R}^{d}$.\qed\end{definition}

@@

\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,RichmanBridges1999,Hamhalter2013}~Given
a vector~$\ket{\psi}\in S^{2}$ with a specified north pole~$\ket{0}\in S^{2}$,
then 
\begin{itemize}
\item $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$ denotes the the
latitude of $\ket{\psi}$.
\item The great circle on $S^{2}$ is the intersection of $S^{2}$ with
a plane containing the center of $S^{2}$.
\item If $0<\theta\left(\ket{\psi}\right)<\frac{\pi}{2}$, there is a unique
great circle tangent to the circle of latitude through $\ket{\psi}$;
we shall call it a East-West great circle through $\ket{\psi}$, and
denoted by $C\left(\ket{\psi}\right)$.
\item A point~$\ket{\psi'}$ in a East-West great circle~$C\left(\ket{\psi}\right)$
is \emph{close to} $\ket{\psi}$ if 
\[
\cos\theta\left(\ket{\psi'}\right)=\ip{0}{\psi'}\le2\ip{0}{\psi}=2\cos\theta\left(\ket{\psi}\right)\textrm{ .}
\]
\end{itemize}
\qed\end{definition}

>>>>

\begin{definition}\cite{Hatcher2001}~The unit sphere in $\mathbb{R}^{d}$
is denoted by $S^{d-1}=\left\{ \ket{\psi}\in\mathbb{R}^{d}\middle|\ip{\psi}{\psi}=1\right\} $.\qed\end{definition}

\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ is
called a \emph{real approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
if
\begin{itemize}
\item $W_{l}\le\sideset{_{\mathbb{R}}}{_{i=0}^{d-1}}\sum f\left(\ket{\psi_{i}}\right)\le W_{r}$
for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
of $\mathbb{R}^{d}$.
\item For any $\lambda\in\mathbb{C}\setminus\left\{ 0\right\} $ and $\ket{\psi}\in S^{d-1}$,
$f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$.
\end{itemize}
\qed\end{definition}

@@

\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,RichmanBridges1999,Hamhalter2013}~Given
a vector~$\ket{\psi}\in S^{2}$ with a specified north pole~$\ket{0}\in S^{2}$,
then 
\begin{itemize}
\item $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$ denotes the the
latitude of $\ket{\psi}$.
\item The great circle on $S^{2}$ is the intersection of $S^{2}$ with
a plane containing the center of $S^{2}$.
\item If $0<\theta\left(\ket{\psi}\right)<\frac{\pi}{2}$, there is a unique
great circle tangent to the circle of latitude through $\ket{\psi}$;
we shall call it a East-West great circle through $\ket{\psi}$, and
denoted by $C\left(\ket{\psi}\right)$.
\item We say taking a small step along an East-West great circle to go from
$\ket{\psi}$ to a point $\ket{\psi'}$ if $\ket{\psi'}\in C\left(\ket{\psi}\right)$
and 
\[
\cos\theta\left(\ket{\psi'}\right)=\ip{0}{\psi'}\le2\ip{0}{\psi}=2\cos\theta\left(\ket{\psi}\right)\textrm{ .}
\]
\end{itemize}
\qed\end{definition}
